The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-06-30 exp-resurgence.tex
Work on Riemann-Hilbert section

%%\textcolor{orange}{[Where does resurgence come in?]}
\subsubsection{Solving Riemann--Hilbert problems}
\begin{todo}[\textbf{A} Read through]\end{todo} \begin{old}Sometimes\end{old} \begin{draft}always\end{draft} level 1 ODEs can be regarded as the \begin{old}local version\end{old} \begin{draft}coordinate expressions\end{draft} of some global operators, namely as meromorphic connections on some principal bundles (also known as \textit{opers}~\cite{BD-opers}). In this case, solutions of the ODE are (local) flat sections for the corresponding connection. Therefore, we could use the theory of meromorphic connections to study ODEs, in particular by solving a Riemann--Hilbert problem. \begin{todo}
    add reference
\end{todo}

To formulate the Riemann--Hilbert problem, we should fix the asymptotic behvaiour of the solution as $z\to0,\infty$ and its discontinuities, namely the Stokes data prescribing the jumps of a frame of solutions across each Stokes ray. Then a solution is given by piecewise analytic function, holomorphic away from the rays and with the prescirbed asymptotics and discontinuities.

In many cases, the solutions of Riemann--Hilbert problems can be found explicitly~\cite{Dubrovin-tt_star,Dubrovin-Heun,GMN1,Tom-RH-1,Tom-RH-conifold,BBS-RH}. \begin{draft}These cases include some Riemann--Hilbert problems arising from level~1 ODEs.\end{draft} For example, in~\cite[Section~6.2.1]{kontsevich2022analyticity} Kontsevich and Soibelman discuss a Riemann--Hilbert problem for thimble integrals using the formalism of analytic wall-crossing structures. As we mention in Section~\ref{borel-reg:explanatory-power} every thimble integral satisfies some ODE. Kontsevich and Soibelman also explain why the asymptotics of these thimble integrals are resurgnt series.

>>>>

%%\textcolor{orange}{[Where does resurgence come in?]}
\subsubsection{Solving Riemann--Hilbert problems}
\begin{todo}[\textbf{A} Read through]\end{todo} \begin{revised}A level~$1$ ODE can be seen as the coordinate expression of a meromorphic connection on a principal bundle---specifically, the kind of meromorphic connection called an {\em oper}~\cite{BD-opers}. Local solutions of the ODE correspond to local flat sections of the connection. We can therefore use the theory of meromorphic connections to study level~$1$ ODEs. In particular, we can solve a level~$1$ ODE by solving a Riemann--Hilbert problem.\begin{todo}[add reference]\end{todo}

To formulate the Riemann--Hilbert problem, we fix the asymptotic behvaiour of the solution at $z = 0$ and $z = \infty$,\end{revised} and we also fix its discontinuities---the Stokes data prescribing the jumps of a frame of solutions across each Stokes ray. Then a solution is given by piecewise analytic function, holomorphic away from the rays and with the prescirbed asymptotics and discontinuities.

In many cases, the solutions of Riemann--Hilbert problems can be found explicitly~\cite{Dubrovin-tt_star,Dubrovin-Heun,GMN1,Tom-RH-1,Tom-RH-conifold,BBS-RH}. \begin{draft}These cases include some Riemann--Hilbert problems arising from level~1 ODEs.\end{draft} For example, in Section~6.2.1 of \cite{kontsevich2022analyticity}, Kontsevich and Soibelman discuss a Riemann--Hilbert problem for thimble integrals using the formalism of analytic wall-crossing structures. As mentioned in Section~\ref{borel-reg:explanatory-power}, every thimble integral satisfies some ODE. Kontsevich and Soibelman also explain why the asymptotics of these thimble integrals are resurgnt series.
